---
title: Saving `VCF`s to artifacts and back again
author:
- name: Aaron Lun
  email: infinite.monkeys.with.keyboards@gmail.com
package: alabaster.se
date: "Revised: September 22, 2022"
output:
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Saving and loading VCFs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
library(BiocStyle)
self <- Githubpkg("ArtifactDB/alabaster.vcf")
knitr::opts_chunk$set(error=FALSE, warning=FALSE, message=FALSE)
```

# Overview 

The `r self` package implements methods to save `VCF` objects to file artifacts and load them back into R.
This refers specifically to the `SummarizedExperiment` subclasses (i.e., `CollapsedVCF` and `ExpandedVCF`) that are used to represent the variant calling data in an R session,
which may contain additional modifications that cannot be easily stored inside the original VCF file.
Check out the `r Githubpkg("ArtifactDB/alabaster.base")` for more details on the motivation and concepts of the **alabaster** framework.

# Quick start

Given a `VCF` object, we can use `saveObject()` to save it inside a staging directory:

```{r}
library(VariantAnnotation)
fl <- system.file("extdata", "structural.vcf", package="VariantAnnotation")
vcf <- readVcf(fl, genome="hg19")
vcf

library(alabaster.vcf)
tmp <- tempfile()
meta <- saveObject(vcf, tmp)

list.files(tmp, recursive=TRUE)
```

We can then load it back into the session with `readObject()`.

```{r}
roundtrip <- readObject(tmp)
class(roundtrip)
```

# Session information {-}

```{r}
sessionInfo()
```

